---
title: "ss_2"
author: "Brandon C. Loudermilk"
date: "August 24, 2015"
output: html_document
---

The R language currently supports three object-oriented systems (S3, S4, & RC) each of which differs in degree of adherence to object-oriented principles (from S3 the weakest to RC the strongest). Wickham provides an indepth discussion of the different [OO systems](http://adv-r.had.co.nz/OO-essentials.html), but in summary, the key differences are:

- **S3** - uses *generic-function* rather than *message-passing* OO; no formal definition of 'class'.
- **S4** - has formal definition of 'class'; supports inheritance; supports multiple dispatch; has '@' operator for setting/getting slots.
- **RC** - implements *message-passing* OO; objects are *mutable*

For the present project (designing a spider solitaire game), I sought to implement the majority of the application in **S4** OO system. In S4, the representation of a class is defined through the `setClass()` function and class objects are instantiated with `new()`. S4 classes have three key properties: (1) a name; (2) a list of of slots/attributes; and (3) optional inheritance information.

In spider solitaire, one of the key classes that will be needed by our application is 'Card'. Let's start by modeling the 'Card' class in the S4 system.

```{r}
library(methods) # Where S4-stuff lives

# a Card has a suit = {(S)pade, (H)eart, (C)lub, (D)iamond }
# a Card has a rank = {1:13}
# a Card can be face_up = {TRUE, FALSE}
# Define class "Card" using setClass() function
Card <- setClass("Card",
         slots = list(suit = "character", 
                      rank = "numeric", 
                      face_up = "logical"))

# Create a 'Card' object
h1 <- new(Class = "Card", suit = "H", rank = 1, face_up = FALSE)
class(h1)
print(h1)
```

As we can see, the default `print()` function doesn't print our object very nicely. Let's see if we can improve this by making use of generic function OO. The plain ole `print()` function you call every day, is in reality a generic function that has specific implementations based on input parameters.

```{r, echo=FALSE}
# Examine the definition of 'print'
print
# We see that "print" is a standardGeneric

# Which has *many* specific implementations
methods("print")

# Let's look at the print for two different objects
df <- data.frame(x=1:10, y = 1:10)
print(df)

fit <- glm(y~., data = df)
print(fit)

# When print(df) is called, it really calls a method print.data.frame(df)
print.data.frame(df)

# S4 Method dispatching entails inspection of the class of the input argument
class(df) <- "glm"
print(df) #Oops, thinks its a glm object and tries to call the wrong function
print("^^eek")
```

Okay, so let's now create a custom print function for our 'Card' class.

```{r}
setMethod("print", "Card"
          , function(x){
            if (x@face_up == TRUE) {
              print(paste0(x@suit,x@rank))
            } else {
              print("---")
            }
          })
print(h1)
```

Rather than adding a specific implementation of an existing method, we can also create our own generic functions. Let's create a generic function called `flip()`, which is used to change the state of a binary attribute (e.g., flip a lightswitch on/off or flip a card/coin over)
```{r}
setGeneric("flip", function(x){
  standardGeneric("flip")
})

setMethod("flip", "Card", function(x){x@face_up <- !(x@face_up)
return(x)
})

# Now we can flip our card over!
h1@face_up
h1 <- flip(h1)
h1@face_up
```

So now we have an S4 class called 'Card'... we also know how to create a new instance of a card (using `new()`) and we know how to create and call generic methods on our object. Finally, we would like to create a custom constructor function that wraps up the underlying call to `new()`.

```{r}
# Define some constants
SUITS <- c("S", "H", "C", "D")
RANKS <- 1:13

# Card constructor
Card <- function(suit, rank, face_up = FALSE) {
  
  # Basic validation
  if(!(suit %in% SUITS)) stop(paste0("Invalid suit : ", suit))
  if (!(rank %in% RANKS)) stop(paste0("Invalid rank : ", rank))  
  
  new(Class = "Card", suit = suit, rank = rank, face_up = face_up)
}

s1 <- Card("S",1)
print(s1)

```