---
title: "ss_3"
author: "Brandon C. Loudermilk"
date: "August 24, 2015"
output: html_document
---

We now have a ~~fully functioning~~ prototype `'Card'` class that has slots for `@suit` and `@rank` as well as a logical `@face_up` that indicates if the card face is 'face up'. I won't do very well to have a bunch of random cards hanging around -- we better package them up into a `'Deck'` class. In the snippet below, we have create a 'Deck' class with a single a single slot called `@cards` which is a list that will hold all the cards in the deck.

```{r}
# Define the 'Deck' class
setClass("Deck",
         slots = list(cards = "list"))

# Let's create a constructor function for 'Deck'

Deck <- function(suits = SUITS, ranks = RANKS, num_suits = 1) {
  cards <- list()
  i <- 1
  for (n in 1:num_suits) {
    for (s in suits) {
      for (r in ranks) {
        card <- Card(suit = s, rank = r)
        cards[[i]] <- card
        i <- i + 1
      }
    }
  }
  new(Class = "Deck", cards = cards)
}
```

Let's create some helper methods that query the deck object. First, let's write a function to return a vector of the suits in the current deck. 

```{r}
setGeneric("getSuits", function(x){
  standardGeneric("getSuits")
})

setMethod("getSuits", "Deck", function(x){
  last <- length(x@cards)
  suits <- c()
  for (i in 1:last) {
    s <- x@cards[[i]]@suit
    if (!(s %in% suits)) {
      suits <- c(suits, s)
    }
  }
return(suits)
})
```


The default `Deck()` constructor will create a 'standard' [French deck](https://en.wikipedia.org/wiki/Playing_card#French_suits) of 4 suits and 13 ranks for 52 cards total. By setting specific arguments, the constructor also allows enough flexibility to create the 'custom' decks found in spider solitaire.
```{r}
# Create a standard 'Deck'
standard_deck <- Deck()

# w/ 52 cards
length(standard_deck@cards)

# and 4 suits 
getSuits(standard_deck)

# Create an 'easy' spider solitaire deck
easy_deck <- Deck(suits = c("S"), ranks = 1:13, num_suits = 8)

# Should have 108 cards
length(easy_deck@cards)

# All of suit 'Spades'
getSuits(easy_deck)
```

At this point we have created a 'Deck' class that can contain 'Cards' objects of varying suits and ranks. A deck of cards isn't very useful however, unless one can shuffle it - importantly, however, we must also be able to replicate this random shuffle. Before write the `shuffle()` function, we need to modify our 'Card' and 'Deck' class so we can confirm that shuffling is working.
```{r}
# Add a unique id to the card
Card <- setClass("Card",
         slots = list(suit = "character", 
                      rank = "numeric", 
                      face_up = "logical",
                      id = "numeric"))

# Create a 'Card' object
h1 <- new(Class = "Card", suit = "H", rank = 1, face_up = FALSE, id = 0)
show(h1)

# During 'Deck' creation create unique ids for each card
Deck <- function(suits = SUITS, ranks = RANKS, num_suits = 1) {
  cards <- list()
  id <- 1
  for (n in 1:num_suits) {
    for (s in suits) {
      for (r in ranks) {
        card <- Card(suit = s, rank = r, face_up = FALSE, id = id)
        cards[[id]] <- card
        id <- id + 1
      }
    }
  }
  new(Class = "Deck", cards = cards)
}

new_deck <- Deck()
# All cards in deck have a unique id 
new_deck@cards[[1]]@id == 1
new_deck@cards[[52]]@id == 52

```

Let's write a quick function so we can visualize the order of a deck, so that we can visualize it when shuffled.
```{r}
setGeneric("getIDs", function(x){
  standardGeneric("getIDs")
})

setMethod("getIDs", "Deck", function(x){
  ids <- c()
  for (i in 1:length(x@cards)) {
    id <- x@cards[[i]]@id
    ids <- c(ids, id)
  }
return(ids)
})

d <- Deck()
getIDs(d)
```

Now we can write a `shuffle()` function. We should be able to visualize it is working by shuffling a deck and then observing a new order of cards as reflected by their unique ids.

```{r}
setGeneric(name="shuffle",
           def=function(deck,seed)
           {
             standardGeneric("shuffle")
           }
)

# Given a seed, return the deck back in a new random card order
setMethod(f="shuffle",
          signature="Deck",
          definition=function(deck, seed)
          {
            deck_size <- length(deck@cards)
            set.seed(seed)
            smpl <- sample(1:deck_size, deck_size)
            
            shuffled_cards <- deck@cards[smpl]
            deck@cards <- shuffled_cards
            return (deck)
          }
)

#create a standard deck
d <- Deck()
getIDs(d)
d <- shuffle(deck = d, seed = 1)
getIDs(d) #shuffle works

```
