---
title: "ss_5"
author: "Brandon C. Loudermilk"
date: "August 25, 2015"
output: html_document
---

We left off on the last post creating the major classes of the spider solitaire game: cards, the deck, piles, and the stack. Before fleshing out this design, I'd like to think a bit about visualization. Now the primary reason for building this game, is to use it to run simulations on, so I primarily need to interact with the system via some sort of batch language. In other words, I don't need a very sophisticated UI, but rather a rudimentary system that I can use to debug the application.  

```{r}
# Pile class
setClass("Pile", 
         slots = list(cards = "list"))

# Pile constructor
Pile <- function(cards = NULL) {
  p <- new(Class="Pile", cards = cards)
  return(p)
}

setGeneric(name="getCards",
           def=function(object, ...)
           {
             standardGeneric("getCards")
           }
)

setMethod(f="getCards",
          signature="Pile",
          definition=function(object, ...)
          {
            return (object@cards)
          }
)

setMethod("show",
          signature = "Pile",
          definition = function(object) {
            cat("An object of class ", class(object), "\n", sep = "")
            cards <- object@cards
            for (c in cards) {
              print(c)
            }
            
            invisible(NULL)
            })
```
asd

```{r}

setMethod("show",
          signature = "Game",
          definition = function(object) {
            cat("An object of class ", class(object), "\n", sep = "")
            g <- object
            
            num_cols <- length(g@piles) # This is 10 piles
            max_cards <- 0
            for ( p in g@piles) {
              num_cards <- length(p@cards)
              if (num_cards > max_cards) {
                max_cards <- num_cards
              }
            }
            
            df <- data.frame(a = character(max_cards),
                             b = character(max_cards),
                             c = character(max_cards),
                             d = character(max_cards),
                             e = character(max_cards),
                             f = character(max_cards),
                             g = character(max_cards),
                             h = character(max_cards),
                             i = character(max_cards),
                             j = character(max_cards), 
                             stringsAsFactors = FALSE)
            
            i <- 1
            for (p in g@piles) {
              cards <- getCards(p) #need to write this method
              j <- 1
              for (card in cards) {
                if (card@face_up == TRUE) {
                  smbl <- paste0(card@suit, card@rank)
                } else {
                  smbl <- "***"
                }
                df[j,i] <- smbl
                j <- j + 1
              }

              i <- i + 1
            }
            show(df)
           
            invisible(NULL)

            })





```


You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
